Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-02-01 docs/msr.tex
almost fixed authors

\hyphenation{op-tical net-works semi-conduc-tor}

@@

\author{
\IEEEauthorblockN{Dimitris Mitropoulos Vassilios Karakoidas Panos Louridas Diomidis Spinellis}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: \{dimitro, bkarak, louridas, dds\}@aueb.gr}
\and
\IEEEauthorblockN{Georgios Gousios}
\IEEEauthorblockA{Department of Software and Computer Technology\\
Delft University of Technology \\
Email: G.Gousios@tudelft.nl}
}

@@

\subsection{Bug Categorisation and Overview}
\label{sec:bug}

\begin{table}
\centering
\caption{Bug Categorisation according to FindBugs}
\label{tbl:bug-categorisation}
\begin{tabular}{l r}
 \hline
Category & Description\\
\hline
Bad Practice & \\
Correctness & \\
Experimental & \\
Internationalisation & \\
Multi-Threaded Correctness & \\
Performance & \\
Style & \\
Security & \\
\hline
\end{tabular}
\end{table}

>>>>

@@

\author{
\IEEEauthorblockN{Dimitris Mitropoulos}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: dimitro@aueb.gr}
\and
\IEEEauthorblockN{Vassilios Karakoidas}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: bkarak@aueb.gr}\\
\and
\IEEEauthorblockN{Panos Louridas}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: louridas@aueb.gr}
\and
\IEEEauthorblockN{Diomidis Spinellis}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: dds@aueb.gr}
\and
\IEEEauthorblockN{Georgios Gousios}
\IEEEauthorblockA{Department of Software and Computer Technology\\
Delft University of Technology\\
Email: G.Gousios@tudelft.nl}
}

@@

\subsection{Overview and Initial Results}
\label{sec:overview}

\begin{figure*}
	\centering
	\includegraphics[scale=0.6]{bug_percent}
	\caption{Bug Percentage in Maven Repository}
	\label{fig:bug-percentage}
\end{figure*}

\begin{table}
\centering
\caption{Bug categorisation according to FindBugs}
\label{tbl:bug-categorisation}
\begin{tabular}{l r}
 \hline
Category & Description\\
\hline
Bad Practice & \\
Correctness & \\
Experimental & \\
Internationalisation & \\
Multi-Threaded Correctness & \\
Performance & \\
Style & \\
Security & \\
\hline
\end{tabular}
\end{table}
